Preprocessing summary

### 2021-01-12 inst/examples/summary.Rmd
Added many auxiliary files

# Read the preprocessed data
df <- readRDS("data/unified/polished/df.Rds")
df.orig <- readRDS("data/unified/polished/df.raw.Rds")
conversions <- readRDS("conversions.Rds")
```

>>>>

# Read the preprocessed data
df <- readRDS("df.Rds")
df.orig <- readRDS("df.raw.Rds")
conversions <- readRDS("conversions.Rds")
```
